Figures

### 2019-07-03 figures/07_model-selection.Rmd
figure resize

```{r tp_summary, fig.height=4}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tp_re}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, pasture RE slope") + theme(legend.position = 0)

@@

```{r tn_summary, fig.height=4}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tn_re}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

@@

gg_hist <- ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) +
  theme(rect = element_rect(fill = "transparent"), 
        strip.background = element_rect(fill = "white"), 
        strip.text = element_text(face = "bold")) +
  facet_wrap(~pretty)

>>>>

```{r tp_summary, fig.width=3.25, fig.height=4}
# lapply(re_brms, function(x) x$formula) 
fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tp_re, fig.width=3.25, fig.height=4.5}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, pasture RE slope") + theme(legend.position = 0)

@@

```{r tn_summary, fig.height=4, fig.width=3.25}
# lapply(re_brms, function(x) x$formula) 
fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

```{r tn_re, fig.width=3.25, fig.height=4.5}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

@@

gg_hist <- ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  cowplot::theme_cowplot() +
  theme(legend.position = 0) +
  theme(rect = element_rect(fill = "transparent"), 
        strip.background = element_rect(fill = "transparent"), 
        strip.text = element_text(face = "bold")) +
  facet_wrap(~pretty)
